Self Regulation Ontology Retest Data Report

### 2017-04-25 SRO_Report.Rmd
fixed coding error in positive transformations

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(jsonlite)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
```

@@

  # transform variables
  # log transform for positive skew
  # positive_subset = log(positive_subset)
  positive_subset = pos_log(positive_subset) #slight divergence from original code
  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
  names(successful_transforms) = c('skew')
  successful_transforms$dv = row.names(successful_transforms)
  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
  successful_transforms = successful_transforms$dv
  successful_transforms = positive_subset[,successful_transforms]
  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)

@@

#### Spearman

@@

Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.

@@

Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?  
The regression suggests that the more measures that went in to the averaging of Spearman's $\rho$'s the lower the mean Spearman $\rho$ for that task. This might suggest that this way of summarizing data might not be a good idea in general or at least that we shouldn't do it for the Spearman correlations.

@@

Bootstrapping

```{r}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}

@@

Bootstrapping everything at once locally would take around four hours.
```{r eval=FALSE}
as.data.frame(numeric_cols) %>%
  mutate(index = 1:n()) %>%
  group_by(index) %>%
  # rowwise()%>% #this works too but the output is nicer the other way
  do(plyr::rdply(2, bootstrap_relialibility(dv_var = as.character(.$numeric_cols), metric = c("icc", "spearman"))))

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(jsonlite)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(digits = 4)
```

@@

  # transform variables
  # log transform for positive skew
  # positive_subset = log(positive_subset)
  # positive_subset = pos_log(positive_subset) #slight divergence from original code
  positive_subset = as.data.frame(apply(positive_subset, 2, pos_log))
  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
  names(successful_transforms) = c('skew')
  successful_transforms$dv = row.names(successful_transforms)
  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
  successful_transforms = successful_transforms$dv
  successful_transforms = positive_subset[,successful_transforms]
  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)

@@

### Spearman

@@

Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? It seems the more measures that goes in to summarizing overall reliability for a task the worse it gets. This would make sense if these variables are intended to measure different things and some are less reliable than others.

@@

Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?  
The same is true for Spearman's correlations as well.

@@

## Transformation effects

```{r}
raw_retest_subs_test_data = raw_test_data[raw_test_data$sub_id %in% raw_retest_data$sub_id,]

raw_numeric_cols = c()

for(i in 1:length(names(raw_test_data))){
  if(is.numeric(raw_test_data[,i])){
    raw_numeric_cols <- c(raw_numeric_cols, names(raw_test_data)[i])
  }
}

raw_rel_df <- data.frame(spearman = rep(NA, length(raw_numeric_cols)),
                     icc = rep(NA, length(raw_numeric_cols)), 
                     eta_sq = rep(NA, length(raw_numeric_cols)),
                     sem = rep(NA, length(raw_numeric_cols)))

row.names(raw_rel_df) <- raw_numeric_cols

for(i in 1:length(raw_numeric_cols)){
  raw_rel_df[raw_numeric_cols[i], 'spearman'] <- get_spearman(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data) 
  raw_rel_df[raw_numeric_cols[i], 'icc'] <- get_icc(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
  raw_rel_df[raw_numeric_cols[i], 'eta_sq'] <- get_eta(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
  raw_rel_df[raw_numeric_cols[i], 'sem'] <- get_sem(raw_numeric_cols[i], t1_df = raw_retest_subs_test_data, t2_df = raw_retest_data)
}

raw_rel_df$dv = row.names(raw_rel_df)
row.names(raw_rel_df) = seq(1:nrow(raw_rel_df))
raw_rel_df$task = 'task'
raw_rel_df[grep('survey', raw_rel_df$dv), 'task'] = 'survey'
raw_rel_df = raw_rel_df %>%
  select(dv, task, spearman, icc, eta_sq, sem)
```

```{r warning=FALSE, message=FALSE}
raw_rel_df %>%
  group_by(task) %>%
  summarise(median_spearman = median(spearman),
            median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n())
```

Plots of change in reliability depending on transformation

```{r}
ggplotly(rel_df %>%
  mutate(dv = gsub(".logTr", "", dv)) %>%
  mutate(dv = gsub(".Re", "", dv)) %>%
  left_join(raw_rel_df, by = 'dv') %>%
  ggplot(aes(spearman.x, spearman.y, color = task.x, label=dv))+
  geom_point()+
  geom_abline(intercept = 0, slope=1)+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("Spearman at t1")+
  ylab("Spearman at t2"))
```

```{r}
ggplotly(rel_df %>%
  mutate(dv = gsub(".logTr", "", dv)) %>%
  mutate(dv = gsub(".Re", "", dv)) %>%
  left_join(raw_rel_df, by = 'dv') %>%
  ggplot(aes(icc.x, icc.y, color = task.x, label=dv))+
  geom_point()+
  geom_abline(intercept = 0, slope=1)+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("ICC at t1")+
  ylab("ICC at t2"))
```

------------------------------------------------------------------------
Bootstrapping

```{r eval=FALSE}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}

@@

Bootstrapping everything at once in this way locally would take around four hours.
```{r eval=FALSE}
as.data.frame(numeric_cols) %>%
  mutate(index = 1:n()) %>%
  group_by(index) %>%
  # rowwise()%>% #this works too but the output is nicer the other way
  do(plyr::rdply(2, bootstrap_relialibility(dv_var = as.character(.$numeric_cols), metric = c("icc", "spearman"))))
